Towards Practical First-Order Model Counting

### 2024-01-26 doc/paper.tex
Some notes regarding the proof of correctness

@@

@@

>>>>

% TODO: mention/describe the arithmetic simplification code

@@

% TODO: describe which compilation rules are currently greedy or non-greedy.

@@

\paragraph{Proof of Correctness}
\begin{enumerate}
  \item Define what it means for a formula to be \emph{consistent}.
        \begin{itemize}
          \item The formula (including the mapping of constants to their
                domains) does not mention a domain together with its subdomain
                (i.e., all mentioned domains are pairwise disjoint).
                Specifically, we can't have a subdomain together with its parent
                domain or a subdomain together with a constant that belongs to
                its parent domain.
          \item The target of \texttt{Ref} must also be a consistent formula.
          \item The initial formula is consistent by definition.
        \end{itemize}
  \item Aim to show that Crane works correctly on all consistent formulas.
  \item Prove that, whenever some compilation rule makes the formula $\phi$
        inconsistent, greedy compilation rules will make $\phi$ consistent again
        before $\phi$ encounters non-greedy compilation rules that depend on
        $\phi$ being consistent.
        \begin{itemize}
          \item In particular, prove that shattering and unit propagation will
                always eliminate the parent domain of the domains introduced by
                atom counting.
          \item Constraint removal only applies when it can eliminate the parent
                domain entirely.
          \item Prove this for a particular assumption about which compilation
                rules are set to be greedy. For the greedy algorithm, although
                all rules are applied in a greedy manner, we still assume that
                greedy rules will be applied before non-greedy rules.
        \end{itemize}
  \end{enumerate}
